When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases\thanks{Part of this paper appeared at IJCAI \citep{DBLP:conf/ijcai/McCreeshPT16}; \cref{section:introduction} has been expanded and \cref{section:models,section:labelled,section:filterverify} are new material.}

### 2017-09-29 paper/paper.tex
Pictures etc

Various general principles have been considered when designing variable and value ordering
heuristics for backtracking search algorithms---one of these is to try to maximise the expected
number of solutions inside any subproblem considered during search \citep{DBLP:conf/cp/GentMPSW96}.  This is
usually done by cheaper surrogates, rather than direct calculation. When branching, both LAD and
Glasgow pick a variable with fewest remaining values in its domain: doing this will generally reduce
the first part of the $\langle Sol \rangle$ equation by as little as possible. When two or more
domains are of equal size, LAD simply breaks ties lexicographically, whereas Glasgow will pick a
variable corresponding to a pattern vertex of highest degree. This strategy was determined
empirically, but could have been derived from the $\langle Sol \rangle$ formula: picking a pattern
vertex of high degree will make the remaining pattern subgraph sparser, which will decrease the
exponent in the second half of the formula, maximising the overall value. LAD does not apply a value
ordering heuristic, but Glasgow does: it prefers target vertices of lowest degree.  Again, this was
determined empirically, but it has the effect of increasing $\langle Sol \rangle$ by increasing the
remaining target density. The VF2 heuristics, in contrast, are based around preserving connectivity,
which gives very little discrimination except on the sparsest of inputs.

>>>>

Various general principles have been considered when designing variable and value ordering
heuristics for backtracking search algorithms---one of these is to try to maximise the expected
number of solutions inside any subproblem considered during search \citep{DBLP:conf/cp/GentMPSW96}.  This is
usually done by cheaper surrogates, rather than direct calculation. When branching, both LAD and
Glasgow pick a variable with fewest remaining values in its domain: doing this will generally reduce
the first part of the $\langle Sol \rangle$ equation by as little as possible. When two or more
domains are of equal size, LAD simply breaks ties lexicographically, whereas Glasgow will pick a
variable corresponding to a pattern vertex of highest degree. This strategy was determined
empirically, but could have been derived from the $\langle Sol \rangle$ formula: picking a pattern
vertex of high degree will make the remaining pattern subgraph sparser, which will decrease the
exponent in the second half of the formula, maximising the overall value. LAD does not apply a value
ordering heuristic, but Glasgow does: it prefers target vertices of highest degree.  Again, this was
determined empirically, but it has the effect of increasing $\langle Sol \rangle$ by leaving as many
vertices as possible available for future use. The VF2 heuristics, in contrast, are based around
preserving connectivity, which gives very little discrimination except on the sparsest of inputs.
